Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-03-10 Milestone_1/01-chap1.Rmd
fix typo 1

However, unlike confirmatory data analysis built upon rigorous statistical procedures, e.g., hypothesis testing, visual diagnostics relies on graphical perception - human’s ability to interpret and decode the information embedded in the graph [@cleveland_graphical_1984], which is to some extent subjective. Further, visual discovery suffers from its unsecured and unconfirmed nature where the degree of the presence of the visual features typically can not be measured quantitatively and objectively, which may lead to over or under-interpretations of the data. One such example is finding an over-interpretation of the separation between gene groups in a two-dimensional projection from a linear discriminant analysis when in fact there are no differences in the expression levels between the gene groups and separation is not an uncommon occurence [@roy_chowdhury_using_2015].

@@

Visual inference was first introduced in a 1999 Joint Statistical Meetings (JSM) talk with the title "Inference for Data Visualizatino" by @buja_inference_1999 as an idea to address the issue of valid inference for visual discoveries of data plots [@gelman_exploratory_2004]. Later, in the Bayesian context, data plots was systematically considered as model diagnostics by taking advantage of the data simulated from the assumed statistical models [@gelman_bayesian_2003; @gelman_exploratory_2004].

@@

In visual inference, a visual discovery is defined as a rejection of a null hypothesis, and the same null hypothesis can be rejected by many different visual discoveries [@buja_statistical_2009]. For model diagnostics, the null hypothesis would be the assumed model, while the visual discoveries would be any findings that are inconsistent with the null hypothesis. The same assumed model, such as classical linear regression model, can be rejected by many reasons with residual plot, including nonlinearity and heteroskedasticity as shown in Figure \@ref(fig:residual-plot-cubic-heter).

@@

In the context of model diagnostics, sampling data from $H_0$ is equivalent to sampling data from the assumed model. As @buja_statistical_2009 suggested, $H_0$ is usually composited by a collection of distributions controlled by nuisance parameters. Since statistical models can have various forms, there is no general solution to this problem, but it sometimes can be reduced to so called "reference distribution" by applying one of the three methods: (i) sampling from a conditional distribution given a minimimal sufficient statistic under $H_0$, (ii) parametric bootstrap sampling with nuisance parameters estimated under $H_0$, and (iii) Bayesian posterior predictive sampling.

@@

The remainder of the report is organised as follows. Chapter \ref{se:research-problem} outlines the three research problems. Chapter \ref{se:overview} gives an overview of the thesis including descriptions of three projects. Chapter \ref{se:project-1} presents the human subject experiments conducted in the first project along with the prototype of the automatic visual inference system. Chapter \ref{se:project-2}

@@

3. Validate and apply the automatic visual inference system to predictive model diagnostics on empirical data.

@@

The third project aims to apply the automatic system to predictive model diagnostics on empirical data. Potential predictive models considered by this research are linear model, generalized linear models and non-parametric regression. Multiple human subject experiments will need to be conducted to validate the effectiveness of the automatic system.

@@

To collect data of human performance on reading residual plot of linear regression model with nonlinearity and heteroskedasticity defects, two human experiments were conducted. Participants of both experiments were recruited using an online platform called Prolific [@prolific_prolific_2022].

@@

The study website was powered by Flask [@grinberg_flask_2018], a web framework written in Python 3 [@van_rossum_python_2009], hosted on PythonAnywhere [@pythonanywhere_pythonanywhere_2022], a web hosting service provider. Due to the limit of the storage on PythonAnywhere, lineup images needed for the website were hosted separately on Github Pages [@gtihub_github_2022-1], a static site hosting service provided by Github [@gtihub_github_2022], stored in private Github repositories. The uniform resource locator (URL) to lineup images were set to be unique random strings such that images can not be accessed by general approaches without knowing the correct URL. This avoided participants seeing the lineup beforehand. The front-end of the website was built using a JavaScript [@flanagan_javascript_2006] library jsPsych [@de_leeuw_jspsych_2015] which is specialized in creating online behavioral experiments. One of the reasons we chose to use this library was it had a modularized but highly customizable template which could record participant's response time automatically. This is essential for us to confirm the quality of the data by checking exceptionally fast or slow responses. Figure \@ref(fig:diagram-experiment) summarizes the online experiment setup.

@@

Next we will discuss the simulation setup for this study. The experiment data was simulated by the use of the programming language `R` [@r_core_team_r_2021]. For the ease of reproducibility, functions to build models, simulate data from models, produce lineup with data, allocate stimulis for subjects and evaluate subject responses from this study are bundled in the package `visage` with a unique object-oriented programming system built upon the environment feature of `R`. In the description of the simulation, corresponding functionalities of the package will be introduced.

@@

This defines a cubic relationship between $\boldsymbol{Y}$, $\boldsymbol{X}$ and $\boldsymbol{Z}$. Meanwhile, to create nonlinearity defect, the null model followed the assumptions of the classical normal linear regression model (CNLRM), fitted by OLS is:
\begin{equation} \label{eq:cubic_null}
\boldsymbol{Y}=\beta_0+\beta_1\boldsymbol{X}+\beta_2\boldsymbol{Z}+\boldsymbol{u},
\end{equation}
where $\boldsymbol{u} \sim N(0,\sigma^2_u\boldsymbol{I})$.

@@

Under the cubic model setting, there is an exact conventional test for testing the nonlinearity defect, which is F-test. For F-test, the null hypothesis is $H_0:a=b=0$, and the alternative hypothesis is $H_1:\text{at least one of them} \neq 0$. During the simulation of the lineup data, the F-statistic and the p-value will be recorded for comparison between the power of conventional test and visual test.

@@

Lemma \@ref(lemma:heter) shows that variance and covariance of the residuals depend on $\boldsymbol{X}$. We could plot the one standard deviation around the residuals to indicate the region about 68% of the residuals should landed on. Figure \@ref(fig:hetershape) illustrates different shapes of residuals undder various values of $a$ and $b$. From the plot, it can be observed that if $a = 0$, the residual plot looks like the shape of butterfly. If $a = \pm 1$, it looks like a triangle, and the sign of $a$ determines the direction of the shape. Parameter $b$ is controlling the strength of the signal. As $b$ increases, the pattern becomes less noisy.

@@

The cubic model involved the use of both $\boldsymbol{X}$ and $\boldsymbol{Z}$. In the simulation, $X_i$, $i=1,...,n$, had equal chance to follow one of the following distributions: $N(0, 0.09)$, $U(-1, 1)$, $Lognormal(0,0.36)/3 - 1$ and $-Lognormal(0,0.36)/3 + 1$. Uniform and normal distribution were symmetric and common. Adjusted lognormal distribution and adjusted negative lognormal distribution provided right-skewed and left-skewed density respectively. These distributions were chosen such that most the realizations will fall between $-1$ and $1$.

The distribution of $Z_i$, $i=1,...,n$, had $50$% chance to be a uniform distribution ranged from $-1$ to $1$, and $50$% chance to be a discrete uniform distribution with $z_n$ outcomes simulated from a uniform distribution ranged from $-1$ to $1$. $z_n$ itself was a discrete uniform distribution with outcomes $\{10,11,12,13,14,15,16,17,18,19,20\}$, which defined the number of possible values $Z_i$ could take. As shown in Figure \@ref(fig:discreteex), this setup would create discreteness in residual plot, which could enrich the pool of visual patterns.

@@

$\boldsymbol{X}$ used in the heteroskedasticity model was a combination of $\boldsymbol{X}$ and $\boldsymbol{Z}$ used in the cubic model. It could be one of the five distributions mentioned above - normal distribution, uniform distribution, adjusted lognormal distribution, adjusted negative lognormal distribution and discrete uniform distribution.

@@

For cubic model, the separation between curves was small. Fitted power of visual test with three to five evaluations were almost identical to each other in regards of effect size. In addition, all five curves peaked at one as effect size increased, suggesting that identification of nonlinearity as a visual task can be completed reliably by human when the effect size is large enough.

@@

According to Table \@ref(tab:rejectfactorcubic), for cubic model, both coefficients of $|a|$ and $|b|$ were positive, which suggested increasing the coefficients of quadric and cubic terms would result in higher visual power. The coefficient of $|c-1|$ was also positive indicating joint effect of multiple regressors on the residual plot decreased the visual power. As expected, the coefficient of $\sigma$ was negative as it controlled the noise level. Lineup simulated with uniform distribution of $\boldsymbol{X}$ had the highest power, followed by negative lognormal, normal, and lognormal. Discreteness in $\boldsymbol{Z}$ decreased the visual power. The coefficient of number of observations was positive, which means larger sample size would lead to higher visual power.

Results of logistic regression for heteroskedasticity is given in Table \@ref(tab:rejectfactorheter). For heteroskedasticity model, the coefficient of $|a|$ was negative, which suggested "butter fly" shape was easier to identify than "triangle" shape. As expected, the coefficient of $b$ was positive. For different distributions of $\boldsymbol{X}$, the one with highest power was uniform distribution, followed by normal, discrete uniform, lognormal and negative lognormal. The coeffient of the number of observations was positive, but it was not significant.

In overall, we did not have any unexpected findings except the visual power related to different distributions of $\boldsymbol{X}$ in cubic model. We expected lineup simulated with uniform distribution would have the highest power, followed by normal, lognormal and negative lognormal, since we observed similar results in pilot study.

@@

Considering there are different approches of AI, it is necessary to clarify the type of AI we aimed to build. Understanding the human thought process or mimicking the human vision mechanism were not of interest in this research. We believed humanly behaviours was enough for demonstrating AI for the problem we concerned. Hence, two of the capacities required by the total Turing test, namely machine learning and computer vision were adopted.

@@

By using this workflow, we were not only able to dramatically reduce the training time, but also able to gain better performance because the pre-trained models we used were trained on a large dataset called ImageNet [@deng_imagenet_2009] with more than 14 million images on 1000 object classes. The famous annual competition ImageNet Large Scale Visual Recognition Challenge (ILSCRV) ran annually by the ImageNet project was a gold standard for evaluating the architecture of computer vision model. Among the leaderboard of ILSCRB, we picked architectures that were handy to implement and with low top-5 error rate. This included VGG16 [@simonyan_very_2015], VGG19 [@simonyan_very_2015], Xception [@chollet_xception_2017], ResNet152V2 [@he_identity_2016] and InceptionV3 [@szegedy_rethinking_2015]. The top-5 error rate is the average number the model failed to include the answer among its top five guesses. The overview of all five transer learning models are given in Table \ref{tab:vi-model-summary}. Note that the depth is the number of layers in the model.

@@

Dropout was primary used as a regularization technique to address overfitting. In training, the dropout layer would randomly temporaliy remove some nodes from the network with fixed probability $p$, which in our case, we used $p = 20$%.

@@

By adopting the techniques developed in query by example content-based image retrieval, we aims to build automatic general-purpose visual inference system based on image comparison in the second project.

# Automatic Visual Infernce for Predictive Model Diagnostics {#se:project-3}

...

# Timeline

\begin{table} \label{tab:timeline}
\centering
\begin{tabular}[t]{ll}
\toprule
\addlinespace[0.5em]
Date & Event\\
\addlinespace[0.5em]
\midrule
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2022}}}\\
\hspace{4em}March & Extend the scope of violations of classical normal linear\\ 
\addlinespace[0.5em]
\hspace{4em} & regression considered by the computer vision model\\
\addlinespace[0.5em]
\hspace{4em}April & Conduct human subject experiment on the extended model\\ 
\addlinespace[0.5em]
\hspace{4em} & defects\\
\addlinespace[0.5em]
\hspace{4em}May & Conclude the first project: draft and submit the first paper\\
\addlinespace[0.5em]
\hspace{4em}June & Review previous studies in image comparison\\
\addlinespace[0.5em]
\hspace{4em}July & Draft a new automatic visual inference system based\\
\addlinespace[0.5em]
\hspace{4em} & on image comparison\\
\addlinespace[0.5em]
\hspace{4em}August - November & Build the automatic system\\
\addlinespace[0.5em]
\hspace{4em}November - December & Conduct human subject experiment for validating the\\
\addlinespace[0.5em]
\hspace{4em} & automatic system\\
\addlinespace[0.5em]
\hspace{4em}December & Attend the Australasian Applied Statistics Conference\\
\addlinespace[0.5em]
\hline
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2023}}}\\
\hspace{4em}January - March & Finish the second project: prepare milestone material and\\
\addlinespace[0.5em]
\hspace{4em} & submit the second paper\\
\addlinespace[0.5em]
\hspace{4em}April - December & Apply the automatic visual inference system to predictive\\
\addlinespace[0.5em]
\hspace{4em} & model diagnostics\\
\addlinespace[0.5em]
\hline
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2024}}}\\
\hspace{4em}January - March & Finish the third project: finalize the thesis\\
\addlinespace[0.5em]
\bottomrule
\end{tabular}
\end{table}

>>>>

However, unlike confirmatory data analysis built upon rigorous statistical procedures, e.g., hypothesis testing, visual diagnostics relies on graphical perception - human’s ability to interpret and decode the information embedded in the graph [@cleveland_graphical_1984], which is to some extent subjective. Further, visual discovery suffers from its unsecured and unconfirmed nature where the degree of the presence of the visual features typically can not be measured quantitatively and objectively, which may lead to over or under-interpretations of the data. One such example is finding an over-interpretation of the separation between gene groups in a two-dimensional projection from a linear discriminant analysis when in fact there are no differences in the expression levels between the gene groups and separation is not an uncommon occurrence [@roy_chowdhury_using_2015].

@@

Visual inference was first introduced in a 1999 Joint Statistical Meetings (JSM) talk with the title "Inference for Data Visualization" by @buja_inference_1999 as an idea to address the issue of valid inference for visual discoveries of data plots [@gelman_exploratory_2004]. Later, in the Bayesian context, data plots was systematically considered as model diagnostics by taking advantage of the data simulated from the assumed statistical models [@gelman_bayesian_2003; @gelman_exploratory_2004].

@@

In visual inference, a visual discovery is defined as a rejection of a null hypothesis, and the same null hypothesis can be rejected by many different visual discoveries [@buja_statistical_2009]. For model diagnostics, the null hypothesis would be the assumed model, while the visual discoveries would be any findings that are inconsistent with the null hypothesis. The same assumed model, such as classical linear regression model, can be rejected by many reasons with residual plot, including non-linearity and heteroskedasticity as shown in Figure \@ref(fig:residual-plot-cubic-heter).

@@

In the context of model diagnostics, sampling data from $H_0$ is equivalent to sampling data from the assumed model. As @buja_statistical_2009 suggested, $H_0$ is usually composited by a collection of distributions controlled by nuisance parameters. Since statistical models can have various forms, there is no general solution to this problem, but it sometimes can be reduced to so called "reference distribution" by applying one of the three methods: (i) sampling from a conditional distribution given a minimal sufficient statistic under $H_0$, (ii) parametric bootstrap sampling with nuisance parameters estimated under $H_0$, and (iii) Bayesian posterior predictive sampling.

@@

The remainder of the report is organised as follows. Chapter \ref{se:research-problem} outlines the three research problems. Chapter \ref{se:overview} gives an overview of the thesis including descriptions of three projects. Chapter \ref{se:project-1} presents the prototype of the automatic visual inference system along with the results of two human subject experiments. Chapter \ref{se:project-2} introduces the general-purpose automatic visual inference system. Chapter \ref{se:project-3} describes the deployment of the automatic system. Chapter \ref{se:timeline} presents the timeline of the three projects.

@@

3. Deploy the automatic visual inference system as an adaptive online application by applying online machine learning.

@@

The third projects aims to package and deploy the automatic system as an adaptive online application such that empirical data can be collected and used in improving the system. Online machine learning technique will be used to update the weights of computer vision models dynamically.

@@

To collect data of human performance on reading residual plot of linear regression model with non-linearity and heteroskedasticity defects, two human experiments were conducted. Participants of both experiments were recruited using an online platform called Prolific [@prolific_prolific_2022].

@@

The study website was powered by Flask [@grinberg_flask_2018], a web framework written in Python 3 [@van_rossum_python_2009], hosted on PythonAnywhere [@pythonanywhere_pythonanywhere_2022], a web hosting service provider. Due to the limit of the storage on PythonAnywhere, lineup images needed for the website were hosted separately on Github Pages [@gtihub_github_2022-1], a static site hosting service provided by Github [@gtihub_github_2022], stored in private Github repositories. The uniform resource locator (URL) to lineup images were set to be unique random strings such that images can not be accessed by general approaches without knowing the correct URL. This avoided participants seeing the lineup beforehand. The front-end of the website was built using a JavaScript [@flanagan_javascript_2006] library jsPsych [@de_leeuw_jspsych_2015] which is specialized in creating online behavioural experiments. One of the reasons we chose to use this library was it had a modularized but highly customizable template which could record participant's response time automatically. This is essential for us to confirm the quality of the data by checking exceptionally fast or slow responses. Figure \@ref(fig:diagram-experiment) summarizes the online experiment set-up.

@@

Next we will discuss the simulation set-up for this study. The experiment data was simulated by the use of the programming language `R` [@r_core_team_r_2021]. For the ease of reproducibility, functions to build models, simulate data from models, produce lineup with data, allocate stimulus for subjects and evaluate subject responses from this study are bundled in the package `visage` with a unique object-oriented programming system built upon the environment feature of `R`. In the description of the simulation, corresponding functionalities of the package will be introduced.

@@

This defines a cubic relationship between $\boldsymbol{Y}$, $\boldsymbol{X}$ and $\boldsymbol{Z}$. Meanwhile, to create non-linearity defect, the null model followed the assumptions of the classical normal linear regression model (CNLRM), fitted by OLS is:
\begin{equation} \label{eq:cubic_null}
\boldsymbol{Y}=\beta_0+\beta_1\boldsymbol{X}+\beta_2\boldsymbol{Z}+\boldsymbol{u},
\end{equation}
where $\boldsymbol{u} \sim N(0,\sigma^2_u\boldsymbol{I})$.

@@

Under the cubic model setting, there is an exact conventional test for testing the non-linearity defect, which is F-test. For F-test, the null hypothesis is $H_0:a=b=0$, and the alternative hypothesis is $H_1:\text{at least one of them} \neq 0$. During the simulation of the lineup data, the F-statistic and the p-value will be recorded for comparison between the power of conventional test and visual test.

@@

Lemma \@ref(lemma:heter) shows that variance and covariance of the residuals depend on $\boldsymbol{X}$. We could plot the one standard deviation around the residuals to indicate the region about 68% of the residuals should landed on. Figure \@ref(fig:hetershape) illustrates different shapes of residuals under various values of $a$ and $b$. From the plot, it can be observed that if $a = 0$, the residual plot looks like the shape of butterfly. If $a = \pm 1$, it looks like a triangle, and the sign of $a$ determines the direction of the shape. Parameter $b$ is controlling the strength of the signal. As $b$ increases, the pattern becomes less noisy.

@@

The cubic model involved the use of both $\boldsymbol{X}$ and $\boldsymbol{Z}$. In the simulation, $X_i$, $i=1,...,n$, had equal chance to follow one of the following distributions: $N(0, 0.09)$, $U(-1, 1)$, $Lognormal(0,0.36)/3 - 1$ and $-Lognormal(0,0.36)/3 + 1$. Uniform and normal distribution were symmetric and common. Adjusted log-normal distribution and adjusted negative log-normal distribution provided right-skewed and left-skewed density respectively. These distributions were chosen such that most the realizations will fall between $-1$ and $1$.

The distribution of $Z_i$, $i=1,...,n$, had $50$% chance to be a uniform distribution ranged from $-1$ to $1$, and $50$% chance to be a discrete uniform distribution with $z_n$ outcomes simulated from a uniform distribution ranged from $-1$ to $1$. $z_n$ itself was a discrete uniform distribution with outcomes $\{10,11,12,13,14,15,16,17,18,19,20\}$, which defined the number of possible values $Z_i$ could take. As shown in Figure \@ref(fig:discreteex), this set-up would create discreteness in residual plot, which could enrich the pool of visual patterns.

@@

$\boldsymbol{X}$ used in the heteroskedasticity model was a combination of $\boldsymbol{X}$ and $\boldsymbol{Z}$ used in the cubic model. It could be one of the five distributions mentioned above - normal distribution, uniform distribution, adjusted log-normal distribution, adjusted negative log-normal distribution and discrete uniform distribution.

@@

For cubic model, the separation between curves was small. Fitted power of visual test with three to five evaluations were almost identical to each other in regards of effect size. In addition, all five curves peaked at one as effect size increased, suggesting that identification of non-linearity as a visual task can be completed reliably by human when the effect size is large enough.

@@

According to Table \@ref(tab:rejectfactorcubic), for cubic model, both coefficients of $|a|$ and $|b|$ were positive, which suggested increasing the coefficients of quadric and cubic terms would result in higher visual power. The coefficient of $|c-1|$ was also positive indicating joint effect of multiple regressors on the residual plot decreased the visual power. As expected, the coefficient of $\sigma$ was negative as it controlled the noise level. Lineup simulated with uniform distribution of $\boldsymbol{X}$ had the highest power, followed by negative log-normal, normal, and log-normal. Discreteness in $\boldsymbol{Z}$ decreased the visual power. The coefficient of number of observations was positive, which means larger sample size would lead to higher visual power.

Results of logistic regression for heteroskedasticity is given in Table \@ref(tab:rejectfactorheter). For heteroskedasticity model, the coefficient of $|a|$ was negative, which suggested "butter fly" shape was easier to identify than "triangle" shape. As expected, the coefficient of $b$ was positive. For different distributions of $\boldsymbol{X}$, the one with highest power was uniform distribution, followed by normal, discrete uniform, log-normal and negative log-normal. The coefficient of the number of observations was positive, but it was not significant.

In overall, we did not have any unexpected findings except the visual power related to different distributions of $\boldsymbol{X}$ in cubic model. We expected lineup simulated with uniform distribution would have the highest power, followed by normal, log-normal and negative log-normal, since we observed similar results in pilot study.

@@

Considering there are different approaches of AI, it is necessary to clarify the type of AI we aimed to build. Understanding the human thought process or mimicking the human vision mechanism were not of interest in this research. We believed humanly behaviours was enough for demonstrating AI for the problem we concerned. Hence, two of the capacities required by the total Turing test, namely machine learning and computer vision were adopted.

@@

By using this workflow, we were not only able to dramatically reduce the training time, but also able to gain better performance because the pre-trained models we used were trained on a large dataset called ImageNet [@deng_imagenet_2009] with more than 14 million images on 1000 object classes. The famous annual competition ImageNet Large Scale Visual Recognition Challenge (ILSCRV) ran annually by the ImageNet project was a gold standard for evaluating the architecture of computer vision model. Among the leaderboard of ILSCRB, we picked architectures that were handy to implement and with low top-5 error rate. This included VGG16 [@simonyan_very_2015], VGG19 [@simonyan_very_2015], Xception [@chollet_xception_2017], ResNet152V2 [@he_identity_2016] and InceptionV3 [@szegedy_rethinking_2015]. The top-5 error rate is the average number the model failed to include the answer among its top five guesses. The overview of all five transfer learning models are given in Table \ref{tab:vi-model-summary}. Note that the depth is the number of layers in the model.

@@

Dropout was primary used as a regularization technique to address overfitting. In training, the dropout layer would randomly temporarily remove some nodes from the network with fixed probability $p$, which in our case, we used $p = 20$%.

@@

By adopting the techniques developed in query by example content-based image retrieval, we aims to build automatic general-purpose visual inference system based on image comparison in the second project. General-purpose means that we will not make any assumption about the type of the plot and the data generating process such that the system will be able to evaluate any lineups asking for selecting the most different plot(s).

# OAVIS: An online automatic visual inference system {#se:project-3}

Online machine learning is a technique to train machine learning model with data arriving in a sequential order. Models trained with online learning can be updated immediately for any new arrival data, which overcomes the drawbacks of the traditional batch learning where training data required to be available prior to the training. It is suitable for large-scale machine learning tasks in real-world data analytics applications [@].

The third projects aims to deploy the automatic visual inference system as an online application at a public-accessible website. The web application will evaluate lineups uploaded by users, and return the $p$-value with the selections made by the system. Meanwhile, as an option, users will be asked to also evaluate the lineup and give their selections. With the user selection data, the system will use online machine learning theory to update the built-in computer vision models such that the performance of the system can be improved.

# Timeline {#se:timeline}

\begin{table} \label{tab:timeline}
\centering
\begin{tabular}[t]{ll}
\toprule
\addlinespace[0.5em]
Date & Event\\
\addlinespace[0.5em]
\midrule
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2021}}}\\
\hspace{4em}March - August & Design the study website and the experiments\\ 
\hspace{4em}September & Apply for human research ethics approval\\ 
\hspace{4em}October & Test the study website\\ 
\hspace{4em}November & Conduct the first two human subject experiments\\ 
\hspace{4em}December & Develop the \textit{R} package \textit{visage}\\ 
\addlinespace[0.5em]
\hline
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2022}}}\\
\hspace{4em}January & Develop the computer vision models\\
\hspace{4em}February & Prepare for the first milestone\\
\hspace{4em}March & Extend the scope of violations of classical normal linear\\ 
\addlinespace[0.5em]
\hspace{4em} & regression considered by the computer vision model\\
\addlinespace[0.5em]
\hspace{4em}April & Conduct human subject experiment for the extended model\\ 
\addlinespace[0.5em]
\hspace{4em} & defects\\
\addlinespace[0.5em]
\hspace{4em}May & Conclude the first project: draft and submit the first paper\\
\addlinespace[0.5em]
\hspace{4em}June & Review previous studies in image comparison\\
\addlinespace[0.5em]
\hspace{4em}July & Draft a new automatic visual inference system based\\
\addlinespace[0.5em]
\hspace{4em} & on image comparison\\
\addlinespace[0.5em]
\hspace{4em}August - November & Build the automatic system\\
\addlinespace[0.5em]
\hspace{4em}November - December & Conduct human subject experiment for validating the\\
\addlinespace[0.5em]
\hspace{4em} & automatic system\\
\addlinespace[0.5em]
\hspace{4em}December & Attend the Australasian Applied Statistics Conference\\
\addlinespace[0.5em]
\hline
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2023}}}\\
\hspace{4em}January - March & Finish the second project: prepare milestone material and\\
\addlinespace[0.5em]
\hspace{4em} & submit the second paper\\
\addlinespace[0.5em]
\hspace{4em}April - December & Deploy the automatic visual inference system as \\
\addlinespace[0.5em]
\hspace{4em} & a web application\\
\addlinespace[0.5em]
\hline
\addlinespace[0.5em]
\multicolumn{2}{l}{\textit{\textbf{2024}}}\\
\hspace{4em}January - March & Finish the third project: finalize the thesis\\
\addlinespace[0.5em]
\bottomrule
\end{tabular}
\end{table}
